---
title: "Assigment - kNN DIY"
author:
  - Danny Bannink (Author)
  - Teun Vlassak (Reviewer)
date: 
```{r}
format(Sys.time(), '%d %B, %Y')
```



output:
   html_notebook:
    toc: true
    toc_depth: 2
---
## Setup library

```{r}
install.packages("XML")
install.packages("rvest")
install.packages("GGally")
library(tidyverse)
library(XML)
library(rvest)
library(GGally)
```

#This is good!

```{r}
install.packages("corrplot")
library("corrplot")
```

#This is good!

### Data Understanding

```{r}
rdf <- as.data.frame(read_html("https://github.com/HAN-M3DM-Data-Mining/data-mining-s1y2223-DannyBannink/blob/master/datasets/KNN-occupancy.csv") %>% html_table(fill=TRUE))
print(rdf) # Look at the results of the gained data
```

#This is good!

### Data Preperation
# Removing 1st column since it has no value
```{r}
cdf <- rdf[,colSums(is.na(rdf))<nrow(rdf)] # Removing first column since it doesn't add any value.
print(cdf) # Look at the new table to test if the codeline works.
```

#This is good!

# Renaming columnnames so all headers are true
```{r}
colnames(cdf)
names(cdf)[1] <- "Date"
names(cdf)[2] <- "Temperature"
names(cdf)[3] <- "Humidity"
names(cdf)[4] <- "Light"
names(cdf)[5] <- "CO2"
names(cdf)[6] <- "Humidity_Ratio"
names(cdf)[7] <- "Occupancy"
head(cdf)
```

#This is good!

# Removing 2nd row since there is now a "character" within the dataset which makes the dataframe unusable for analysis
```{r}
knn <- cdf[-1,]
head(knn)
```

#This is good!


## Changing data format from charachter to numeric
```{r}
knn$Temperature <- as.numeric(knn$Temperature)
knn$Humidity <- as.numeric(knn$Humidity)
knn$Light <- as.numeric(knn$Light)
knn$CO2 <- as.numeric(knn$CO2)
knn$Humidity_Ratio <- as.numeric(knn$Humidity_Ratio)
knn$Occupancy <- as.numeric(knn$Occupancy) 
```

#This is good!

## Getting rid of the 'date' column in order to be able to plot a correlationdiagram
```{r}
knn1 <- select(knn, -1) # Selecting the whole dataframe minus the 'date' column
head(knn1) # Checking if the codeline works
format(knn1) # To see if all the needed values are numeric (requirement for plotting the data)
```

#This is good!


## Summary knn measurements
```{r}
summary(knn[c("Temperature", "Humidity", "Light", "CO2", "Humidity_Ratio")])
```

#This is good!

## Adjusting datatype of 'Occupancy' to 'factor' 
```{r}
knn2 <- knn$Occupancy <- factor(knn$Occupancy, levels = c("0", "1"), labels = c("Empty", "Occupied")) %>% relevel("Occupied")
head(knn2, 10)
knnlabel <- knn2
```

#This is good!

## Counts for Occupancy label
```{r}
cntDiag <- table(knn$Occupancy)
propDiag <- round(prop.table(cntDiag) * 100 , digits = 1)

cntDiag
```

#This is good!

## Prop diagram
```{r}
propDiag
```

#This is good!

```{r}
str(knn1)
```

#This is good!

## Normalize differences in ranges per column
```{r}
normalize <- function(x) { # Function takes in a vector
  return ((x - min(x)) / (max(x) - min(x))) # distance of item value - minimum vector value divided by the range of all vector values
}

testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")
```

#This is good!

```{r}
cat("testSet2:", testSet2, "\n")
```

#This is good!

```{r}
cat("Normalized testSet1:", normalize(testSet1), "\n")
```
```{r}
cat("Normalized testSet2:", normalize(testSet2))
```
## Test normalization function
```{r}
nrow <- dim(knn1)[5]
````

#This is good!

```{r}
knn3_n <- sapply(5,
                    function(x) {
  normalize(knn1[,x])
}) %>% as.data.frame()
```

# knn3_n <- sapply(5:nrow,function(x)normalize(knn1[,x])
#Removed :nrow from the code.

```{r}
summary(knn1[c("Temperature", "Humidity", "Light", "CO2", "Humidity_Ratio")])
```
#summary(knn1[c("Temperature", "Humidity", "Light", "CO2", "Humidity_Ratio")])
#removed knn3_n and added knn1.



```{r}
str(knn1)
```

#This is good!


### Data Modelling
# Check occupancy if light is 0
```{r}
nrow(knn[knn$Light == 0 & knn$Occupancy == 0,]) ## Total count when there is 0 Occupancy compared to 'Light' (5160)
```

#This is good!

```{r}
knn %>% count(Light) ## Amount of total '0 values' in column 'Light' (5160)
```

#This is good!

```{r}
model1 <- glm(Occupancy~Temperature+Humidity+Light+CO2+Humidity_Ratio, family = binomial, data=knn)
model1
```

#This is good!


## Correlation Matrix
```{r}
ggcorplot(cor(knn), hc.order = TRUE, type = "lower") # Here you can see that there is a big correlation between the amount of light and the occupation of the office. 
```

#This is good!

## Confusion matrix
```{r}
levels(knn1$Occupancy)=0:1
head(knn1$Occupancy)
table(knn1$Occupancy)
```

#This is good!

## Multiple regression
```{r}
model1 <- lm(Occupancy~Temperature+Humidity+Light+CO2+Humidity_Ratio, data=knn1)
summary(model1)
```

#This is good!

## Filtering data
```{r}
knn1 <- knn %>% filter(Light > 0) ## Deleting all 0 values within the column 'Light' since no occupation is there if there's no Light
head(knn1) %>% view(knn1) ## To see if the codeline worked (It worked)
```

#This is good!

## Check if  filtering the '0 values'  in column Light worked
```{r}
knn1 %>% count(Light) ## Amount of total '0' values in column 'Light'
## It worked
```

#This is good!


#Error 1:

# knn3_n <- sapply(5,
#                   function(x) {
#  normalize(knn1[,x])
# }) %>% as.data.frame()

# knn3_n <- sapply(5:nrow,function(x)normalize(knn1[,x])
#Removed :nrow from the code.

#Error 2:

#summary(knn1[c("Temperature", "Humidity", "Light", "CO2", "Humidity_Ratio")])

#summary(knn1[c("Temperature", "Humidity", "Light", "CO2", "Humidity_Ratio")])
#removed knn3_n and added knn1.

